### 2018-02-07 submission/manuscript.Rmd
change legends to OR

**Figure 2: Relative Risk for Adenoma or Carcinoma based on Bacterial Community Metrics in Stool.** A) Community-based relative risk for adenoma. B) Community-based relative risk for carcinoma. Colors represent the different variable regions used within the respective study.

**Figure 3: Top 5 Genera that Decrease and Increase Relative Risk for Lesion.** A) Adenoma relative risk in stool. B) Carcinoma relative risk in stool. C) Adenoma relative risk in tissue. D) Carcinoma relative risk in tissue. For all panels the relative risk was also compared to whether one, two, three, or four of the CRC-associated genera were present.

>>>>

**Figure 2: Odds Ratio for Adenoma or Carcinoma based on Bacterial Community Metrics in Stool.** A) Community-based odds ratio for adenoma. B) Community-based odds ratio for carcinoma. Colors represent the different variable regions used within the respective study.

**Figure 3: Top 5 Genera that Decrease and Increase Odds Ratio for Lesion.** A) Adenoma odds ratio in stool. B) Carcinoma odds ratio in stool. C) Adenoma odds ratio in tissue. D) Carcinoma odds ratio in tissue. For all panels the odds ratio was also compared to whether one, two, three, or four of the CRC-associated genera were present.

### 2018-02-07 submission/manuscript.tex
change legends to OR

\textbf{Figure 2: Relative Risk for Adenoma or Carcinoma based on
Bacterial Community Metrics in Stool.} A) Community-based relative risk
for adenoma. B) Community-based relative risk for carcinoma. Colors
represent the different variable regions used within the respective
study.

\textbf{Figure 3: Top 5 Genera that Decrease and Increase Relative Risk
for Lesion.} A) Adenoma relative risk in stool. B) Carcinoma relative
risk in stool. C) Adenoma relative risk in tissue. D) Carcinoma relative
risk in tissue. For all panels the relative risk was also compared to
whether one, two, three, or four of the CRC-associated genera were
present.

>>>>

\textbf{Figure 2: Odds Ratio for Adenoma or Carcinoma based on Bacterial
Community Metrics in Stool.} A) Community-based odds ratio for adenoma.
B) Community-based odds ratio for carcinoma. Colors represent the
different variable regions used within the respective study.

\textbf{Figure 3: Top 5 Genera that Decrease and Increase Odds Ratio for
Lesion.} A) Adenoma odds ratio in stool. B) Carcinoma odds ratio in
stool. C) Adenoma odds ratio in tissue. D) Carcinoma odds ratio in
tissue. For all panels the odds ratio was also compared to whether one,
two, three, or four of the CRC-associated genera were present.
